\documentclass{resume}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Daniel Spiridonov}
\address{+7(936) 505-1245 \\ Moscow, Russia}
\address{\href{mailto:sprv-4@yandex.ru}{sprv-4@yandex.ru} \\ \href{https://github.com/cop1cat}{github.com/cop1cat}}

\begin{document}

%----------------------------------------------------------------------------------------
%	ABOUT ME
%----------------------------------------------------------------------------------------
\begin{rSection}{ABOUT ME}
Specialist in machine learning and data analysis. Experience in deploying models and pipelines to production. Participated in projects and hackathons.
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\begin{rSection}{EDUCATION}
{\bf Specialist Degree, "Computer Security" \\ National Research University Higher School of Economics (HSE)}, \hfill {2022-2028}\\
\textit{Moscow Institute of Electronics and Mathematics}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\begin{rSection}{TECHNICAL SKILLS}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming languages: & Python, C++ \\
Machine Learning: & CatBoost, XGBoost, Transformers, LangChain, PyTorch, Scikit-Learn \\
Data Analytics: & Pandas, NumPy, SQL \\
ML Ops: & Docker, Git, Airflow, MLflow, GitLab CI/CD, monitoring (Prometheus, Grafana) \\
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------
\begin{rSection}{WORK EXPERIENCE}

\textbf{ML Engineer}  
\textit{RT-Information Security} | Dec 2024 – Present  
\begin{itemize}
    \itemsep -3pt {}
    \item Development and implementation of ML models for automating SOC center processes.
    \item Design and implementation of data collection and enrichment systems for model operation.
    \item Deployment of infrastructure components for production model operation.
    \item Documentation automation and metrics monitoring.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}

\textbf{Claw Engine: AI Module}  
\textit{HSE}  
\begin{itemize}
    \itemsep -3pt {}
    \item Developed a library for training game agents using SAC and integrated it into Unity.
    \item Created a service for summarizing game reviews for game designers.
\end{itemize}

\end{rSection}

\end{document}
